Supporting Information: Time Series Modeling of Solute Transport in an H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-12-11 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Adjusting visualizations
New figures and analysis to paper. Parallelization to scripts

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}

@@

@@

@@

  We validated our approach to simulating trajectory realizations by testing
  it against analytical solutions to the mean first passage time of a Brownian
  particle with 2 absorbing boundaries.

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{array}
\usepackage{multirow}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

@@

  \section{Solute hopping and trapping behavior}\label{section:sfbm_other_solutes}

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_trajectories.pdf}
  \caption{}\label{fig:GCL_solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/distributions_sfbm.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_GCL.pdf}
  \caption{}\label{fig:GCL_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_powerlaw.pdf}
  \caption{}\label{fig:GCL_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{GCL_hop_acf.pdf}
  \caption{}\label{fig:GCL_hop_acf}
  \end{subfigure}
  \caption{For ethylene glycol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
  for ethylene glycol. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
  in the main text for a more detailed discussion.}\label{fig:GCL_anticorrelated_hops}
  \end{figure}

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_trajectories.pdf}
  \caption{}\label{fig:ACH_solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/distributions_sfbm.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_ACH.pdf}
  \caption{}\label{fig:ACH_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_powerlaw.pdf}
  \caption{}\label{fig:ACH_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ACH_hop_acf.pdf}
  \caption{}\label{fig:ACH_hop_acf}
  \end{subfigure}
  \caption{For acetic acid: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
  for acetic acid. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
  in the main text for a more detailed discussion.}\label{fig:ACH_anticorrelated_hops}
  \end{figure}

  \begin{figure}
  \centering
  %BJC3: included radial distance from pore center because I could. But does that make it look bad?
  % /figures/solute_trajectories.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_trajectories.pdf}
  \caption{}\label{fig:MET_solute_trajectories}
  \end{subfigure}
  % Next 3: /figures/distributions_sfbm.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison_anomalous_MET.pdf}
  \caption{}\label{fig:MET_hop_distribution_comparison}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_powerlaw.pdf}
  \caption{}\label{fig:MET_powerlaw}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{MET_hop_acf.pdf}
  \caption{}\label{fig:MET_hop_acf}
  \end{subfigure}
  \caption{For methanol: (a) representative $z$-coordinate center of mass trajectories, (b) hop 
  length distributions, (c) dwell time distributions and (d) hop autocorrelation functions
  for methanol. See Figure~\ref{M-fig:anticorrelated_hops} and Section~\ref{M-section:AD_parameterization}
  in the main text for a more detailed discussion.}\label{fig:MET_anticorrelated_hops}
  \end{figure}

  \section{Tabular Anomalous Diffusion Parameters}\label{section:tabular_AD_params}

  % BJC: note to self -- modes are flipped in simulation output because 
  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0. 
  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
  \hline 
  \end{tabular}
  \caption{To create a 1 mode model for each solute, we parameterized a pure power
  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
  law tails and higher values of $\lambda$ truncate the distribution at lower
  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
  function ($\gamma(H)$) to describe the degree of correlation between hops. 
  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
  \end{table}

  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  \multicolumn{7}{|c|}{2 Mode Model} \\\hline
                & Parameters                               & Mode & Urea         & Ethylene Glycol &  Methanol    & Acetic Acid \\
  \hline
                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.90         & 0.58         \\\cline{3-7}
  Dwell         &                                          & 2    & 0.38         &  0.48           & 0.58         & 0.33         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.04, 0.0006 & 0.41, 0.0026 \\\cline{3-7}
                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.30, 0.0054 & 0.00, 0.0021 \\\hline
                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.45         & 0.32         \\\cline{3-7}
  Hop           &                                          & 2    & 0.24         &  0.23           & 0.32         & 0.17         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.31, 1.97   & 0.21, 1.91   \\\cline{3-7}
                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.85   & 0.09, 1.50   \\\hline
  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           & 0.30         & 0.34         \\\cline{3-7}
  \hline 
  \end{tabular}
  \caption{The two model parameterizes solute behavior in the pores and tails separately. 
  Generally, movement is much more restricted in the tail region. To create a 2 mode model,
  we generated a set of parameters based on solute behavior as function of distance from
  the pore center. Mode 1 corresponds to solute behavior within 0.75 nm of the pore center
  and mode 2 corresponds to behavior greater than or equal to 0.75 nm from the pore center.
  Note that we used the same Hurst parameter for both modes due to a low number of 
  sufficiently long sequences of hops in each mode. See Table~\ref{table:sfbm_params} for
  descriptions of the parameters.}\label{table:sfbm_params_2mode}
  \end{table}

@@

  \section{Tabular MSDDM parameters}\label{section:msddm_params}

  \begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
  \hline
  & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
  State & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$   & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$ \\\hline
  1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045      & 0.11  & 1.56     & 0.052    & 0.10 & 1.78     & 0.035    \\
  2     & 0.06  & 1.80     & 0.033    & 0.09 & 1.75     & 0.037      & 0.07  & 1.63     & 0.043    & 0.08 & 1.88     & 0.032    \\
  3     & 0.11  & 1.88     & 0.030    & 0.11 & 1.86     & 0.030      & 0.02  & 1.80     & 0.036    & 0.04 & 2.00     & 0.030    \\
  4     & 0.10  & 1.95     & 0.027    & 0.04 & 1.91     & 0.028      & 0.02  & 1.75     & 0.036    & 0.04 & 2.00     & 0.027    \\
  5     & 0.19  & 1.34     & 0.048    & 0.15 & 1.40     & 0.062      & 0.10  & 1.28     & 0.074    & 0.13 & 1.47     & 0.048    \\
  6     & 0.15  & 1.45     & 0.040    & 0.11 & 1.52     & 0.040      & 0.03  & 1.50     & 0.042    & 0.09 & 1.70     & 0.038    \\
  7     & 0.15  & 1.61     & 0.032    & 0.05 & 1.60     & 0.040      & 0.28  & 1.20     & 0.043    & 0.08 & 1.77     & 0.031    \\
  8     & 0.11  & 1.71     & 0.028    & 0.05 & 1.74     & 0.030      & 0.04  & 1.83     & 0.037    & 0.01 & 2.00     & 0.030    \\
  T     & 0.34  & 1.42     & 0.036    & 0.37 & 1.44     & 0.045      & 0.35  & 1.45     & 0.057    & 0.34 & 1.54     & 0.040    \\\hline
  \end{tabular}
  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
  trajectories and used them to generate realizations of our MSDDM model. The states
  are defined in Table~\ref{table:states} except state T which describes the transition
  emissions.}\label{table:msddm_params}
  \end{table}

@@

%  We validated our approach to simulating trajectory realizations by testing
%  it against analytical solutions to the mean first passage time of a Brownian
%  particle with 2 absorbing boundaries.

  \begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{mfpt_curves_brownian.pdf}
  \caption{}\label{fig:mfpt_curve_brownian}
  \end{figure}
